
\documentclass[krantz1,ChapterTOCs]{krantz}
\usepackage{fixltx2e,fix-cm}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{subfigure}
\usepackage{makeidx}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{listings}

\frenchspacing
\tolerance=5000

\makeindex

\include{frontmatter/preamble} %place custom commands and macros here

\begin{document}

\frontmatter

\title{STEM Outreach Activities... 
}
\author{Scott Turner}

\maketitle

%\include{frontmatter/dedication}
%\cleardoublepage
\setcounter{page}{7} %previous pages will be reserved for frontmatter to be added in later.
\tableofcontents
%\include{frontmatter/foreword}
%\include{frontmatter/preface}
\listoffigures
\listoftables
%\include{frontmatter/contributor}
%\include{frontmatter/symbollist}

\mainmatter
\part{Web-based VR and AR}
\include{chapters/chapter1/ch1}
\include{chapters/chapter2/ch2}
\part{Physical Computing}
\include{chapters/ChapterP1/chp1}
\part{Computational Thinking}
\include{chapters/chapterCT1/chct1}
\part{Artificial Intelligence}

\bibliography{}
\bibliographystyle{plain}
Barr, D., Harrion, J., and Conery, L. (2011) Computational Thinking: A Digital Age Skill for Everyone Leading and Learning with Technology, ISTE, March/April 2011 [accessed via http://www.csta.acm.org/Curriculum/sub/CurrFiles/LLCTArticle.pdf on 26/12/2015]
 
Barr, V. and Stephenson, C. (2011) Bringing Computational Thinking to K-12, ACM Inroads, Vol 2. No 1, pp 48 - 54 [accessed via http://csta.acm.org/Curriculum/sub/CurrFiles/BarrStephensonInroadsArticle.pdf on 26/12/2015]
https://doi.org/10.1145/1929887.1929905
 
Computing at School (2013) Computing in the National Curriculum: A guide for primary teachers [accessed via http://www.computingatschool.org.uk/data/uploads/CASPrimaryComputing.pdf on 13/3/2016]
 
Denning, Peter J. (2009) Beyond Computational Thinking, Communications of the ACM Vol 52, Issue 6, pp 28 - 30 [accessed via http://sgd.cs.colorado.edu/wiki/images/7/71/Denning.pdf on 26/12/2015]
 
DfE: Department for Education (2013) National Curriculum in England: computing programmes of study
 
Freedman, J. (2015) Cycloid Drawing Machine [online] URL: https://www.kickstarter.com/projects/1765367532/cycloid-drawing-machine accessed on 3/3/2016.
 
Google. 2016 Project Jacquard [online] URL: https://www.google.com/atap/project-jacquard/ accesed on:1/3/2016.
 
Knuth, D. 1968. Preface, The Art of Programming vol 1., Boston: Addison-Wesley.
 
Knuth, D. 1996. Foreword. In: Petkovsek, M., Wilf, H., Zeilberger, D. A=B.. Natick: A K Peters/CRC Press, vii.
 
Koetsier, T., 2001. On the prehistory of programmable machines: Musical automata, looms, calculators. Mechanism and Machine Theory, 36(5), 589-603.
https://doi.org/10.1016/S0094-114X(01)00005-2
 
Menegus, B (2016) CDMS: Built with Processing [online] URL: http://wheelof.com/sketch/ accessed on 4/3/2016
 
MoMA. 2012. MoMA| Video Games [online] URL: http://www.moma.org/explore/inside_out/2012/11/29/video-games-14-in-the-collection-for-starters/ accessed on: 1/3/2016.
 
Papert, S (1993) The children's machine: Rethinking schools in the age of the computer. New York: Basic books
 
Pearson M (2011) Generative Art: A practical guide using Processing, New York: Manning, 3-12
 
Selby, C. and Woollard, J. (2013) Computational thinking: the developing definition University of Southampton [accessed via http://eprints.soton.ac.uk/356481/7/Selby_Woollard_bg_soton_eprints.pdf on 26/12/2015]
 
The Art Story (2016) Sol LeWitt [online] http://www.theartstory.org/artist-lewitt-sol.htm accessed on: 6/3/2016
 
Wing, J. (2006) Computational Thinking Communications of the ACM Vol 49 pp 33 - 35 [accessed via https://www.cs.cmu.edu/~15110-s13/Wing06-ct.pdf on 26/12/2015]
https://doi.org/10.1145/1118178.1118215
 
Wing, J. (2011) Computational Thinking - What and Why The Link - News from the School of Computer Science, Issue 6.0, Spring 2011 [accessed via http://www.cs.cmu.edu/sites/default/files/11-399_The_Link_Newsletter-3.pdf on 26/12/2015]
 
Liukas L (2015) Activity 7 The Robots Hello Ruby - Adventures in Coding, New York: Feiwel and Friends, 94-97.
 
Schofield, S (2016) Generative Artworks [online] URL: http://www.simonschofield.net
 
Turner S (2016) 3 'Art' Scratch Projects [online] URL: http://compuationalthinking.blogspot.co.uk/2016/03/3-of-my-scratch-projects-for-week.html accessed on: 12/3/2016.

\printindex

\end{document}
